Intended Table of Contents Thesis

### 2013-02-28 Chapters/Chapter1.tex
More on HMM
Removed linebreaks
Extend Literature review
Working on the literature review. For now discussed a few papers quite
elaborate. Goal is to discuss more papers and group them.

\section{Literature review}
Look into earlier application mentioned in the literature to this kind of 
problems. Look for similarities in the problem and address where the 
techniques used fail or are not applicable.

@@

\section{Learning \LaTeX{}}

>>>>

\input{./Chapters/Chapter1/literature_review}

@@

\section{System architecture}

*** [GRAPHICS diagram: sensors --> signal pre-processing --> feature extraction --> analysis [* segmentation, * labeling] --> conclusions]
